### 2022-03-18 paper/localpsf.tex
restructuring paper

Since our end goal is constructing a H-matrix, we are freed from strict adherence to the product-convolution format. This allows us to modify the product-convolution approach to address well-known deficiencies. In particular, product-convolution approximations are based on an assumption of local translation invariance, while our method is based on an assumption that we call ``normalized local mean displacement invariance,'' which is more general than local translation invariance, and includes both low rank approximation and local translation invariance as special cases (see Section \ref{sec:local_mean_displacement_invariance}). Also, product-convolution approximations have a well-known issues near boundaries called boundary artifacts, which are caused by the boundary artifically ``cutting off'' impulse responses. The product-convolution method requires one to extend the impulse responses outside of the domain where they are undefined. Various extension techniques have been used, such as extension by zero, and reflection across the boundary, yet no known extension technique is fully satisfactory \cite{BOUNDARYETENSION}. In our method we do not have an issue with boundary artifacts because we temporarily exclude impulse responses from the approximation procedure whenever the approximation procedure attempts to evaluate the impulse response at a location where it is undefined. In exchange for these benefits, our approximation can no longer be written as a weighted sum of convolution operators, so we cannot apply our approximation to vectors via the FFT. But this is fine because our approximation is an H-matrix, which can be applied to vectors even faster.

>>>>

Since our end goal is constructing a H-matrix, we are freed from strict adherence to the product-convolution format. This allows us to modify the product-convolution approach to address well-known deficiencies. Product-convolution approximations are based on an assumption of local translation invariance \cite{LOCATRANSLATIONINVARIANCE}, while our method is based on an assumption that we call ``normalized local mean displacement invariance,'' which is more general than local translation invariance, and includes both low rank approximation and local translation invariance as special cases (see Section \ref{sec:local_mean_displacement_invariance}). Also, product-convolution approximations have a well-known issues near boundaries called boundary artifacts, which are caused by the boundary artifically ``cutting off'' impulse responses. The product-convolution method requires one to extend the impulse responses outside of the domain where they are undefined. Various extension techniques have been used, such as extension by zero, and reflection across the boundary, yet no known extension technique is fully satisfactory \cite{BOUNDARYETENSION}. In our method we do not have an issue with boundary artifacts because we temporarily exclude impulse responses from the approximation procedure whenever the approximation procedure attempts to evaluate the impulse response at a location where it is undefined. In exchange for these benefits, our approximation can no longer be written as a weighted sum of convolution operators, so we cannot apply our approximation to vectors via the FFT. But this is fine because our approximation is an H-matrix, which can be applied to vectors even faster.
